Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-09 article/article.Rmd
Commit 2024-06-09 23:11

First, we evaluated the performance of the modelled $\text{GHI}_\text{ref}$ in
relation to the measured GHI for different levels of atmospheric clearness, by using
in the RTM the monthly climatological AOD and WC, less their respective standard
deviations.
the atmospheric level of clearness we have created as reference, in relation to the
measured GHI data, and choose as a representative of the clear sky radiation, the
case where
$\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
($\text{GHI}_\text{CSm}$).
These values represent a typical atmosphere in Thessaloniki, with low load of
aerosols and humidity, which are the main factor that attenuate the GHI, excluding
clouds.  To create the upper limit of CE identification, we used a value relative to
clear sky irradiance
($`r 100*(C4_cs_ref_ratio-1)`\,\%$)
with an additional constant offset of
$`r C4_GLB_diff_THRES`\,\text{W}/\text{m}^2$,
as described in Equation\nobreakspace\ref{eq:CE4}).
\begin{equation}
\text{CE} : \text{E}_\text{i} > `r C4_GLB_diff_THRES` + `r C4_cs_ref_ratio` \cdot \text{E}_\text{CSm,i} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
\end{equation}
where: $\text{E}$ the measured irradiance, $\text{E}_\text{CSm}$ the selected
modelled clear sky irradiance, and $i$ each of the one-minute observation.  This is
the criterion of our CE identification.

>>>>

First, we evaluated the performance of the modelled $\text{GHI}_\text{ref}$ in
relation to the measured GHI for different levels of atmospheric clearness, by using
in the RTM the monthly climatological AOD and WC, less their respective standard
deviations.
<!-- $\tau_{\text{cs}} = \tau_{500\text{nm}} - 1\sigma$ and $w_{h\text{cs}} = w_h - 1\sigma$
($\text{GHI}_\text{CSm}$). -->
These values represent typical atmosphere in Thessaloniki, with lower than average load of
aerosols and humidity, which are the main factor that attenuate the GHI, excluding
clouds. 
To create the upper limit of CE identification, we used a value relative to
clear sky irradiance
($`r 100*(C4_cs_ref_ratio-1)`\,\%$)
with an additional constant offset of
$`r C4_GLB_diff_THRES`\,\text{W}/\text{m}^2$,
as described in Equation\nobreakspace\ref{eq:CE4}).
\begin{equation}
\text{CE} : \text{E}_\text{i} > `r C4_GLB_diff_THRES` + `r C4_cs_ref_ratio` \cdot \text{E}_\text{CSm,i} \,\,[\text{W}/\text{m}^2] \label{eq:CE4}
\end{equation}
where: $\text{E}$ the measured irradiance, $\text{E}_\text{CSm}$ the selected
modelled clear sky irradiance, and $i$ each of the one-minute observation.  This is
the criterion of our CE identification.
